Gafo-cc data processing

### 2022-12-12 analysis/gafo-cc-data-processing.Rmd
fix touch screen stanford

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(screen == "touchscreen", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)
```

@@

```{r}
write_csv(data,"../data/gafo-cc-clean-data.csv")
```

>>>>

```{r}
data_stanford <- read.csv("../../raw_data/gafo-cc/stanford/tidy_data_extra.csv")%>%
  mutate(subjID = paste0("S",subjID),
         community = "stanford",
         screen = ifelse(screen == "yes", 1, 0),
         touchscreen = ifelse(touchscreen == "yes", 1, 0),
         browserVersion = factor(browserVersion),
         targetPosition = factor(targetPosition))%>%
  select(-touchScreen)%>%
  rename(ageinyears = age)%>%
  rename_all(tolower)
```

@@

```{r}
write_csv(data,"../data/gafo-cc-clean-data-incl-fam.csv")
```
